Transparency of COVID-19-related research in medical journals

### 2022-04-12 manuscript_covid_transparency.qmd
Update manuscript_covid_transparency.qmd

>>>>

In comparison to other studies on the transparency of COVID-19 related research is difficult due to different methodology and scale of our research. However, it seems that data sharing was little less common than in our sample than what was the proportion detected in the begininning of the pandemic measured by the investigation of associated data in PubMed Central (https://doi.org/10.1007/s11192-021-03971-6). In addition, the proportion of studies in our stidy study was lower than in COVID-19 related preprints shared via medRxiv and bioRxiv (https://link.springer.com/article/10.1007/s11192-022-04346-1#ref-CR9 ).
